Trends of SDR in Thessaloniki

### 2023-07-03 Article.Rmd
Commit 2023-07-03 13:17

```{r trendALL, echo=F, out.width='.70\\linewidth', fig.cap="Anomaly (\\%) of the daily SDR relative to climatological values for 1993 - 2023  `r year(min(ALL_1_daily_DESEAS$Date))` to `r year(max(ALL_1_daily_DESEAS$Date))`. The black line shows the long term trend for all-sky conditions."}
knitr::include_graphics("./images/LongtermTrends-2.png")
```

@@

<!-- \FloatBarrier -->

@@

<!-- \FloatBarrier -->
<!-- 
## Zenith angle dependency and seasons of the year.
-->

<!-- \FloatBarrier -->

>>>>

more about trend in relation to other trends

```{r trendALL, echo=F, out.width='.70\\linewidth', fig.cap=paste0("Anomaly (\\%) of the daily SDR relative to climatological values for ", year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)), ". The black line shows the long term trend for all-sky conditions.")}
knitr::include_graphics("./images/LongtermTrends-2.png")
```

@@

@@

<!-- 
## Zenith angle dependency and seasons of the year.
-->
